Supporting Information

### 2018-04-11 SupportingInformation.Rmd
typo

In addition to [basic unit tests](https://github.com/sghosh89/BIVAN/blob/master/Tests.Rmd), we 
also tested our statistics by testing whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and 
$\Dsq_u-\Dsq_u$ revealed the asymmetry of tail dependence known to be present in data simulated
from various copulas. Normal and Frank copula families 
are known to have symmetric tail dependence,
i.e., strengths of dependence in the lower and upper tails are the same, for all copulas
in these families [@nelsen2007_copula]. Clayton copulas are known to have stronger lower- than 
upper-tail dependence. And survival Clayton copulas, being rotations of Clayton copulas by 
$180^\circ$, have stronger upper- than lower tail dependence [@nelsen2007_copula].
Using the `iRho` function from the `copula` package, for each of the four families normal, 
Frank, Clayton, and survival Clayton, we obtained parameters for which the expected value of 
Spearman's $\rho$ was, separately, $0,0.1,0.2,...,0.9$. For each copula family and for each 
of the selected parameter values we generated  $n$ points, 100 times, and thereby computed 100 values of the 
statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_u$. This exercise 
was repeated, separately, 
for $n=1000$ and for $n=35$, these cases being chosen, respectively, to reflect asymptotic behavior of the 
statistics and their behavior on the small datasets which are common in some fields
of ecology. The mean and standard error of the three difference statistics were computed for 
each copula family, parameter value, and value of $n$, and results were plotted against 
Spearman's rho (Figures \ref{fig_stat_testing35} and \ref{fig_stat_testing1000}), 
the expectation being that the difference statistics would be positive for 
Clayton copulas and negative for survival Clayton copulas (except for the case of $\rho=0$, a 
boundary case of these families corresponding to independence), and not significantly different 
from $0$ (we used a $t$-test with a significance threshold of $0.05$) for Frank and normal 
copulas. These expectations were fullfilled (Figures \ref{fig_stat_testing35} and 
\ref{fig_stat_testing1000}).

>>>>

In addition to [basic unit tests](https://github.com/sghosh89/BIVAN/blob/master/Tests.Rmd), we 
also tested our statistics by testing whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and 
$\Dsq_u-\Dsq_l$ revealed the asymmetry of tail dependence known to be present in data simulated
from various copulas. Normal and Frank copula families 
are known to have symmetric tail dependence,
i.e., strengths of dependence in the lower and upper tails are the same, for all copulas
in these families [@nelsen2007_copula]. Clayton copulas are known to have stronger lower- than 
upper-tail dependence. And survival Clayton copulas, being rotations of Clayton copulas by 
$180^\circ$, have stronger upper- than lower tail dependence [@nelsen2007_copula].
Using the `iRho` function from the `copula` package, for each of the four families normal, 
Frank, Clayton, and survival Clayton, we obtained parameters for which the expected value of 
Spearman's $\rho$ was, separately, $0,0.1,0.2,...,0.9$. For each copula family and for each 
of the selected parameter values we generated  $n$ points, 100 times, and thereby computed 100 values of the 
statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$. This exercise 
was repeated, separately, 
for $n=1000$ and for $n=35$, these cases being chosen, respectively, to reflect asymptotic behavior of the 
statistics and their behavior on the small datasets which are common in some fields
of ecology. The mean and standard error of the three difference statistics were computed for 
each copula family, parameter value, and value of $n$, and results were plotted against 
Spearman's rho (Figures \ref{fig_stat_testing35} and \ref{fig_stat_testing1000}), 
the expectation being that the difference statistics would be positive for 
Clayton copulas and negative for survival Clayton copulas (except for the case of $\rho=0$, a 
boundary case of these families corresponding to independence), and not significantly different 
from $0$ (we used a $t$-test with a significance threshold of $0.05$) for Frank and normal 
copulas. These expectations were fullfilled (Figures \ref{fig_stat_testing35} and 
\ref{fig_stat_testing1000}).
